String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-05 2023-1-19/sections/algorithms.tex
solving nonemp of cefa

\paragraph*{Step 2.} For each $i \in [n]$, view the transitions $(q, \myvec{0}, q')$ in $\cB'_i$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, then remove the $\varepsilon$-transitions from $\cB'_i$, determinize and minimize the resulting NFA.  \qed

>>>>

\paragraph*{Step 2.} For each $i \in [n]$, we view the transitions $(q, \myvec{0}, q')$ in $\cB'_i$ as $\varepsilon$-transitions $(q, \varepsilon, q')$, then remove the $\varepsilon$-transitions from $\cB'_i$, determinize the resulting NFA, and minimize it.  \qed
